\LARGE \bf Blockchain for routing correctness?

### 2018-07-21 paper.tex
fixed bloom filter section

There are other attacks on blockchain: nothing at stake attack (for POS), sybil attacks, and quantum computers. Briefly, nothing at stake is the problem that block producers do not have any incentive to choose one block, and therefore, will mine after any block as long as they are confident that the blocks before the one they are mining will be accepted by the network. The worry is that miners will mine on top of forks in order to increase the likelihood of a payout, and this does not solve the double spend problem. Sybil attacks occur when malicious nodes cut of honest nodes from the network [Heilman 2015), but it is hard to successfully do if the P2P network is interconnected well (from good seeding). Quantum computers are only a problem if the signature algorithms that are used in transactions are based on the discrete log problem (RSA or ECC) because Shor’s algorithm makes it computationally feasible to factor large numbers (Shor 1994). Hash functions are not as vulnerable to quantum computers as signatures are because key sizes only have to be doubled.

@@

\section{Bloom Filters}
A bloom filter is a data structures used for determining elements in a group. False negatives are impossible and false positives are probabilistic depending on the number of cells and elements in the bloom filter (Bloom 1970).

Bloom filters are used in BM-BGP to provide information on what destination IP addresses have a different AS path. An AS can choose any AS and see if at least one of the paths to any destination prefix has been updated in a specific block on the blockchain. The AS does this by seeing if the IP address is in the bloom filter.

>>>>

There are other attacks on blockchain: nothing at stake attack (for POS), sybil attacks, and quantum computers. Briefly, nothing at stake is the problem that block producers do not have any incentive to choose one block, and therefore, will mine after any block as long as they are confident that the blocks before the one they are mining will be accepted by the network. The worry is that miners will mine on top of forks in order to increase the likelihood of a payout, and this does not solve the double spend problem. Sybil attacks occur when malicious nodes cut of honest nodes from the network (Heilman 2015), but it is hard to successfully do if the P2P network is interconnected well (from good seeding). Quantum computers are only a problem if the signature algorithms that are used in transactions are based on the discrete log problem (RSA or ECC) because Shor’s algorithm makes it computationally feasible to factor large numbers (Shor 1994). Hash functions are not as vulnerable to quantum computers as signatures are because key sizes only have to be doubled.

@@

\section{Bloom Filters}
A bloom filter is a data structure used for determining elements in a group. False negatives are impossible and false positives are probabilistic depending on the number of cells and elements in the bloom filter (Bloom 1970).

Bloom filters are used in BM-BGP to provide information on what IP addresses have at least one new "best path" for a destination IP addresses prefix of an AS. An AS can choose any AS and see if at least one of the paths to any destination prefix has been updated in a specific block on the blockchain. The AS does this by seeing if the IP address is in the bloom filter. The specific new best path is represented in the indexed merkle tree along with the other best paths in the correct position in the merkle tree.
